% verso: colophon / impressum
\thispagestyle{empty}
\vspace*{11cm}
\section*{Imprint}

\textit{Echo-aware signal processing for audio scene analysis}\\
Copyright \textcopyright{} 2020 by \theauthor{}.\\
All rights reserved. Compiled at home, printed in France.\\

\section*{Colophon}
This thesis was typeset using \LaTeX{} and the \texttt{memoir} documentclass.
It is based on Aaron Turon's thesis \emph{Understanding and expressing scalable concurrency}\footnote{\url{https://people.mpi-sws.org/~turon/turon-thesis.pdf}}
(as re-implemented by Friedrich Wiemer\footnote{\url{https://github.com/pfasante/phd_thesis}}),
itself a mixture of \texttt{classicthesis}\footnote{\url{https://bitbucket.org/amiede/classicthesis/}} by Andr\'e Miede and \texttt{tufte-latex}\footnote{\url{https://github.com/Tufte-LaTeX/tufte-latex}},
based on Edward Tufte's \emph{Beautiful Evidence}.\\[0.5\baselineskip]

Graphics and plots are made with PGF/Ti\emph{k}Z, Matplotlib, Mathcha and Excalidraw.
Icons are downloaded from the \url{www.flaticon.com/}
The bibliography was processed by Biblatex.\\[0.5\baselineskip]

The body text is set to 10/14pt (long primer) on a 26pc measure.d
The margin text is set to 8/9pt (brevier) on a 12pc measure.
\library{Linux Libertine} acts as both the text and display typeface.

% recto: dedication or epigraph
\thispagestyle{empty}
\vphantom{.}
\vfill
\begin{dedication}
	A nonna Leti,\\
	\textit{``Lavati le man e va a lavorare!''};
	\vfill
	a nonna Carla,\\
	\textit{``Uuuuuurrrrrcaaaaaaa, che brao ció!''};
\end{dedication}

\thispagestyle{empty}
\vphantom{.}
\vfill
{%
	\flushright{}
	\textsc{Empress Ropes}\sidenote{\itshape en.$\rightarrow$it.$\rightarrow$lat.},
	\\like Morpheus, see you create absurd world;\sidenote{\itshape and sweet mirages.}
	\\like Atlas, you hold up physical worlds;\sidenote{\itshape and walls.}
	\\like Angeróna, you heal from sadness;\sidenote{\itshape and separate noises.}
	\\like Diana, you points arrow and directions;\sidenote{\itshape the closest ref. to vectors and DoA.}
	\\like Urania, you help didascalic work;\sidenote{\itshape papers and thesis.}

	\mynewline
	Unlike Narciso: reflections and echoes won't fool me,
	\\unlike Echo: I answer to you.

	\mynewline
	Deviank, Ikitan, Maishi, Quolcat protect her.
	\\\hfill--- per Giorgia \textsc{Cantisani}
}
\vfill
\vfill