\newcommand{\synopsisDesign}{
    In this chapter the mock valve modelling and prototyping is discussed from conception to completion. Different approaches are disccused in regards to the steps the core design went through;
    \begin{itemize}
        \item Flat Valve: The simplest approach involves creating a flat valve model with leaflets cut to proportion. This design is straightforward to fabricate and provides a basic representation of the \gls{TV} form.
        \item Ballooned Valve: A more anatomically accurate design involves creating a balloon-shaped valve similar to regurgitant valves. This approach aimed to mimic the physiological behavior of the \gls{TV} more closely in the diseased state.
        \item Ballooned Valve with Chordae Tendineae: Building upon the previous design, this approach incorporates chordae tendineae to simulate the \gls{TV}'s complex structure more accurately with practical considerations to how the valve would be modelled, fully represenatively or a simple tri-leaflet valve.
        \item Anatomical Valve without Chordae Tendineae: This approach involved converting \gls{CT} scans of an anatomical valve models, providing a highly realistic representation of the \gls{TV} capturing the likeness very proportionally.
    \end{itemize}
    As well as the design of the other components such as the chordae tendineae and fixturing design.

}

\newcommand{\synopsisDiscussion}{
    In this discussion, the good and bad of the methodology and the results obtained from the testing of a tricuspid valve rig are discussed. The focus is on the challenges encountered and the insights gained from the design and manufacturing processes, particularly in the areas of mold die design and valve prototyping. The successful coaptation and functional testing of the valve, the challenges in achieving anatomical accuracy due to material properties and design limitations, and the durability and functionality of the chordae tendineae.
}